Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-26 sections/eval.tex
Update on Overleaf.

>>>>

\changwan{
To evaluate the capabilities of Finch in graph applications, we its performance for two fundamantal graph applications: Breadth-first search (BFS) and Bellman-Ford single-source shortest path. For scale-free graphs where the distribution of node degrees follows a power-law distribution and a diameter is very short, direction-optimization~\cite{} is crucial to achiceve high-performance. Direction-optimized BFS uses push and pull traversal to efficiently explore graphs. Push traversal starts from the source node, pushing neighboring nodes into the queue. Pull traversal starts from the target node, exploring predecessors (parents).

}
